% !TEX program = xelatex

\documentclass[]{willguthrie-resume}
	\usepackage{fancyhdr}
    \pagestyle{fancy}
    \fancyhf{}
    \usepackage{tikz}
\begin{document}
 
\firstname{Will}
\lastname{Guthrie}
\phone{(647) 984-8115}
\email{william.guthrie@mail.mcgill.ca}
\website{linkedin.com/in/william-guthrie}
\github{Will-Guthrie} 
\header

\noindent\makebox[\linewidth]{\rule{0.94\paperwidth}{0.4pt}}

\hspace*{-\parindent}%
\begin{minipage}[t][][b]{0.33\textwidth}~

	\section{Education}
	\subsection{McGill University}
	\descript{Software Engineering \\ Minor in East Asian Studies}
	\content{Graduated April 2020}
	\sectionsep

	\section{Course Work}
	\subsection{Undergraduate}
	\content{Computer Science}
	Algorithms \& Data Structures \\
	Software Design \\
	Programming Lang \& Paradigms \\
	Database Systems \\
	Software Architecture \\
	Operating Systems \\
	Concurrent Programming \\
	Software Delivery \\
	\content{Mathematics}
	Linear Algebra \\
	Discrete Structures \\
	Calculus \\
	\sectionsep

	\section{Skills}
	\subsection{Programming}
	\content{Languages}
	Python \tb Java \tb C \tb C++ \tb SQL \tb OCaml \\
	\content{Technologies}
	Git \tb Docker \tb CMake \tb Maven \tb Jenkins \tb HTML \tb CSS \tb Bootstrap \\
	\content{Libraries/Frameworks}
	Pandas \tb NumPy \tb pyodbc \tb SQLAlchemy \tb Matplotlib \tb Angular \\
	\sectionsep

	\subsection{General}
	\content{Languages}
	English (Native) \tb French (Fluent) \tb Japanese (Basic) \\
	\content{Design}	
	Adobe Design Suite \tb AutoCAD
	\sectionsep

	\section{Interests}
	\content{Hobbies}
	Food \tb D\&D \tb Motorcycling \tb MTG \tb Skateboarding \tb Travel \\
	\content{Fitness}
	Skiing \tb Swimming \tb Weight Lifting \tb Rock Climbing \tb Yoga \\
	\content{Creative}
	Cooking \tb Baking \tb Clothing \tb Ceramics

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

	\vspace{\topsep}
	\section{Experience}

	\project{Software Engineer}{Hillsdale Investment Management}{May 2020 - Present}
	\vspace{\topsep} % Hacky fix for awkward extra vertical space
	\begin{tightemize}
		\item Integrating previously developed Python projects with new Angular front-end.
		\item Working to replace previously used SQL logic with new SQLAlchemy data-object model.
	\end{tightemize}

	\project{Software Engineering Intern}{Hillsdale Investment Management}{May 2019 - August 2019}
	\begin{tightemize}
		\item Architected \& built Python applications saving over 30 days/year of Portfolio Manager time.
		\item Sped up a pre-existing data analysis process by over 10 times.
		\item Helped company transition to modern version control standards using GitLab.
	\end{tightemize}

	\project{President}{Reboot McGill}{Mar 2019 - Apr 2020}
	\begin{tightemize}
		\item Led an e-waste recycling and refurbishing non-profit responsible for shipping over 100 orders per year.
		\item Created standardized treatment procedures for a variety of common hardware and software problems.
		\item Designed and directed workshops for members on a variety of different technologies (Docker, Git, etc.).
	\end{tightemize}

	\project{Financial Officer}{Computer Taskforce}{May 2017 - Apr 2020}
	\begin{tightemize}
		\item Managed finances of a student technology service with revenues over \$150k/year.
		\item Co-ordinated with the rest of the executive team to provide printing services, laptop rentals, in-house web hosting, and more.
		\item Services used by over 3,000 McGill students per semester.
	\end{tightemize}

	\project{CS Tutor}{McGill CSUS Helpdesk}{Jan 2020 - Apr 2020}
	\begin{tightemize}
		\item Tutored other students in Computer Science.
		\item Clearly communicated technical concepts to an audience having difficulty with the subject. 
		\item Winner of the TEAM award.
	\end{tightemize}

	
	\sectionsep
	\section{Projects}

	\project{SFS}{Simple File System}{}
	\begin{tightemize}
		\item Created a single directory file system in C.
		\item Used bitwise logic to compress the size of the inode status table and free block bitmap by a factor of 32.
		\item Designed to be mountable using a disk emulator and FUSE.
	\end{tightemize}

	\project{Patacat}{Simple Calming Game}{}
	\begin{tightemize}
		\item Listen to lofi music while patting a variety of cats that appear on screen.
		\item Frontend Javascript project created for McHacks 2019.
		\item Winner of the hackathon's Best Designed award.
	\end{tightemize}


\end{minipage}
\end{document}
